---
title: "Exploring the BRFSS data"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `brfss2013`. Delete this note when before you submit 
your work. 

```{r load-data}
load("brfss2013.RData")
```



* * *

## Part 1: Data

As a part of a national survey, we are given data collected without the use of random sampling 
* * *

## Part 2: Research questions

**Research quesion 1:**

Length of Sleep (sleptim1) vs Cancer (chcocncr)

**Research quesion 2:**

**Research quesion 3:**


* * *

## Part 3: Exploratory data analysis

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note when before you submit your work.

**Research quesion 1:**

Plots
Summary statistics
Narrative

```{r}
sleep.cancer.data = brfss2013 %>% 
  filter(!is.na(sleptim1))%>% 
  filter(!is.na(chcocncr))
```



**Research quesion 2:**

```{r}

```



**Research quesion 3:**

```{r}

```

